### 2017-12-04 manuscript.rmd
fixed typo in code

#Nectophore position SIMMAP setup
necto_pos_data = cdata[which(cdata$Nectosome.position != "None"),]
necto_pos = necto_pos_data$Nectosome.position
names(necto_pos) = rownames(necto_pos_data)
NectoPosTree = drop.tree(ultratree, which(!(ultratree$tip.label %in% names(necto_pos))))
make.simmap(NectPosTree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim
#print("SIMMAP Nectophore Types")
```

>>>>

#Nectophore position SIMMAP setup
necto_pos_data = cdata[which(cdata$Nectosome.position != "None"),]
necto_pos = necto_pos_data$Nectosome.position
names(necto_pos) = rownames(necto_pos_data)
NectoPosTree = drop.tip(ultratree, which(!(ultratree$tip.label %in% names(necto_pos))))
make.simmap(NectoPosTree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim
#print("SIMMAP Nectophore Types")
```
